---
title: "Experiment: Boat Harvest Implementation"
subtitle: "Describing the model run when boat-based harvest is amplified above incidental levels"
date: "`r format(Sys.time(), '%B %d, %Y')`"
---

### The Narrative

This Model Run is for a scenario where managers open harvest of seals in the gauntlet by fishing vessels during the Coho fishery. This is modeled similarly to incidental fishery take but at a higher exploitation rate. 

### Run the Model

Parameters listed below are altered from the base run parameterization to simulate the management scenario.

```{r, setup, include = FALSE}
rm(list=ls())
library(knitr)
library(flextable)
library(kableExtra)
knitr::opts_knit$set(root.dir = '~/GitHub/PinnipedCaseStudies')
```

```{r, set pars, include = FALSE}
source("Functions/01_predictFish.R")
source("Functions/makeArray.R")
source("Functions/createHarvestPlan.R")

## Load Data Files and Setup Functions 
source("Ballard/02_Prep_Ballard_salmon_data.R")

## Set Parameters and Create Variables
source("Ballard/03_set_pars.R")
```

```{r set scenario pars, message = FALSE, warning = FALSE}

# adjust parameters for management scenario
steepness_H <- 5 # how quick does it saturate (higher = slower)
efficiency <- 0.125 # what prop of seals are they capable of taking

```

```{r, run loop, include = FALSE}
source("Ballard/04_initialize_variables.R")

## Load Function Files
source("Ballard/05_salmonSpeciesUpdate.R")
source("Functions/decideForagingDestination.R")
source("Functions/collusion.R")
source("Functions/rungeKutta_3.R")
source("Functions/getHarvested.R")
source("Functions/learnX.R")
source("Functions/learnY.R")
source("Functions/type3FuncRes.R")
source("Functions/linearFuncRes.R")
source("Functions/updateLearning.R")

## Run the Loop
source("Ballard/06_The_Loop.R")

## Plots
source("Functions/makePlots.R")
source("Functions/Plots_Pv.R")
source("Functions/Plots_Ej.R")
source("Functions/Plots_Zc.R")
source("Functions/Plots_salmon.R")
source("Functions/Plots_responses.R")
```

### Description of Parameterization

This scenario is focused on the effects of a different management strategy that changes the quantity of seal harvest. Removals occur on days when the coho fishery is open in the gauntlet. The harvest strategy is still boat-based like incidental harvest but it is more aggressive as it is focused on seal removal directly not incidentally as in the base run.

Removals occur from day `r harvest_open` - `r harvest_close`.
When there are `r num_seals` in the Pv, `r num_zc` Californias, and `r num_ej` Stellers in the source pool, pinniped presence at the Gauntlet is as follows:

```{r gauntlet pinnipeds plot, echo = FALSE}
plot_seals + plot_ej + plot_zc

```


...and when there are 40 individual pinnipeds at the Gauntlet, removals are a type 2 function as follows:

```{r harvest response plot, echo = FALSE}
fishers <- 0:max_fishers
plot(fishers, getHarvested(day_plan = "Boat", list_gauntlet_seals = 1:40, 
                           num_fishers = fishers, steepness = steepness_H, 
                           efficiency = efficiency, round = F), ylab = "Harvested Pinnipeds")
```

Here's the (kinda) full parameter list:
```{r parameter table, echo = FALSE, message = FALSE, warning = FALSE}
parameters <- data.frame(rbind(start_loop, end_loop, days, num_seals, num_seals_2_copy, sockeye_escape_rate, chinook_escape_rate, coho_escape_rate, min_fishers, max_fishers, fishery_open, fishery_close, sockeye_fish_rate, chinook_fish_rate, coho_fish_rate, natural_mort, Cmax, Cmax_ej, Cmax_zc, alpha))
colnames(parameters) <- c("Value")
kable(parameters) %>% kable_styling(full_width = F)
```

### Things to Note

The harvest efficiency is set at `r efficiency`, which represents both the proportion of pinnipeds in the gauntlet that are available to harvesters multiplied by the proportion of pinnipeds that harvesters are able to kill of the ones they attempt. In the Locks, fishers are only operating above the Locks in the ship canal, so the only pinnipeds that are available to them are the ones that go above the Locks in pursuit of fish (est. 25% of seals, no sea lions). I then assume that fishers kill 50% of the pinnipeds they shoot at. This results in a `r efficiency` harvest efficiency for boat-based effort by Muckleshoot fishers.

```{r pinniped harvest plot, echo = FALSE}
plot_H + plot_H_ej + plot_H_zc
```

The total harvested pinnipeds are as follows under this parameterization:

```{r harvest table, echo = FALSE}
kable(data.frame(Pv = sum(H), Ej = sum(H_ej), Zc = sum(H_zc))) %>% kable_styling(full_width = F)
```


The fate of the sockeye, Chinook, and coho are as follows under this parameterization:

```{r salmon escapement, echo = FALSE}
salmon_fates <- rbind(salmon_escapement, salmon_catch, salmon_eaten)
salmon_fates$O <- c("Escape", "Catch", "Predated")
kable(salmon_fates) %>% kable_styling(full_width = F)
```
