---
title: "Parameter Manipulation"
output: ioslides_presentation
date: "`r Sys.Date()`"
---

```{r setup, message = FALSE, echo = FALSE, warning = FALSE}
knitr::opts_knit$set(root.dir = '~/GitHub/PinnipedCaseStudies')
library(knitr)
library(kableExtra)

fig.height <- 3
fig.width <- 6
font_size <- 12

source("Functions/01_predictFish.R")
source("Functions/makeArray.R")
source("Functions/createHarvestPlan.R")
source("Functions/decideForagingDestination.R")
source("Functions/collusion.R")
source("Functions/rungeKutta_3.R")
source("Functions/getHarvested.R")
source("Functions/learnX.R")
source("Functions/learnY.R")
source("Functions/type3FuncRes.R")
source("Functions/linearFuncRes.R")
source("Functions/updateLearning.R")
```

## Purpose

This presentation is meant to document single parameter manipulations. The main comparison responses are the number of seals at the Gauntlet and the number of salmon escaped total of each species.

## The Base Run Realm

```{r base run realm, message = FALSE, echo = FALSE, warning = FALSE, fig.height = fig.height, fig.width = fig.width}

source("Ballard/02_Prep_Ballard_salmon_data.R")
source("Ballard/03_set_pars.R")
source("Ballard/04_initialize_variables.R")

source("Ballard/assembleLegosBallard.R")

(plot_seals + theme_classic()) / (eaten_sp_plot+ theme_classic())
salmon_escapement <- data.frame(Run = "Base", Sockeye = escape_sockeye[days], Chinook = escape_chinook[days], Coho = escape_coho[days])

base_salmon_escapement <- salmon_escapement
kable(salmon_escapement, caption = "Escaped Salmon") %>% kable_styling(full_width = F, font_size = font_size)
```


## num_seals

```{r num_seals, message = FALSE, echo = FALSE, warning = FALSE, fig.height=fig.height, fig.width = fig.width}

source("Ballard/02_Prep_Ballard_salmon_data.R")
source("Ballard/03_set_pars.R")
num_seals_list <- seq(from = 1, to = 200, by = 25)
num_Ej_list <- seq(from = 1, to = 200, by = 25)
num_Zc_list <- seq(from = 1, to = 200, by = 25)

Escape <- data.frame(Seals = 0, Sockeye = 0, Chinook = 0, Coho = 0)
for(i in 1:length(num_seals_list)){
  num_seals <- num_seals_list[i]
  num_ej <- num_Ej_list[i]
  num_zc <- num_Zc_list[i]
  source("Ballard/04_initialize_variables.R")
  source("Ballard/assembleLegosBallard.R")
  Escape[i,] <- data.frame(Seals = num_seals, salmon_escapement)
}

Escape <- data.frame(Escape)

plot_escape_manipulations <- ggplot(data = Escape, aes(x = Seals)) +
  geom_line(aes(y = Chinook), color = "seagreen", lwd = 1.2) + 
  geom_line(aes(y = Coho), color = "goldenrod", lwd = 1.2) + 
  geom_line(aes(y = Sockeye), color = "salmon", lwd = 1.2) +
  geom_vline(xintercept = 50, lwd = 2, color = "gray", linetype = 3) +
  labs(y = "Salmon Escaped", x = "Number of Seals in Source Pool") +
  theme_classic()
plot_escape_manipulations

escape_4_tab <- rbind(Escape[1,], Escape[nrow(Escape)/2,], Escape[nrow(Escape),])
escape_4_tab <- escape_4_tab %>% rename_at("Seals", ~ "Run")
escapement_table <- rbind(base_salmon_escapement, escape_4_tab)

kable(escapement_table, caption = "Escaped Salmon") %>% kable_styling(full_width = F, font_size = font_size)

```



## prop_specialists

```{r prop_specialists, message = FALSE, echo = FALSE, warning = FALSE, fig.height=fig.height, fig.width = fig.width}

source("Ballard/02_Prep_Ballard_salmon_data.R")
source("Ballard/03_set_pars.R")

prop_specialists_list <- seq(0, 1, 0.2)

Escape <- data.frame(Prop = 0, Sockeye = NA, Chinook = NA, Coho = NA)
for(i in 1:length(prop_specialists_list)){
  prop_specialists <- prop_specialists_list[i]
  source("Ballard/04_initialize_variables.R")
  source("Ballard/assembleLegosBallard.R")
  Escape[i,] <- data.frame(Prop = prop_specialists, salmon_escapement)
}

Escape <- data.frame(Escape)

plot_escape_manipulations <- ggplot(data = Escape, aes(x = Prop)) +
  geom_line(aes(y = Chinook), color = "seagreen", lwd = 1.2) + 
  geom_line(aes(y = Coho), color = "goldenrod", lwd = 1.2) + 
  geom_line(aes(y = Sockeye), color = "salmon", lwd = 1.2) +
  geom_vline(xintercept = 0.1, lwd = 2, color = "gray", linetype = 3) + 
  labs(y = "Salmon Escaped", x = "Proportion of Seal Pop that are Specialists") +
  theme_classic()
plot_escape_manipulations

escape_4_tab <- rbind(Escape[1,], Escape[nrow(Escape)/2,], Escape[nrow(Escape),])
escape_4_tab <- escape_4_tab %>% rename_at("Prop", ~ "Run")
escapement_table <- rbind(base_salmon_escapement, escape_4_tab)

kable(escapement_table, caption = "Escaped Salmon") %>% kable_styling(full_width = F, font_size = font_size)

```

## alpha (search and capture rate)

```{r alpha, message = FALSE, echo = FALSE, warning = FALSE, fig.height=fig.height, fig.width = fig.width}

source("Ballard/02_Prep_Ballard_salmon_data.R")
source("Ballard/03_set_pars.R")

alpha_list <- seq(0, 1, 0.1)

Escape <- data.frame(Alpha = 0, Sockeye = NA, Chinook = NA, Coho = NA)
for(i in 1:length(alpha_list)){
  alpha <- alpha_list[i]
  source("Ballard/04_initialize_variables.R")
  source("Ballard/assembleLegosBallard.R")
  Escape[i,] <- data.frame(Alpha = alpha, salmon_escapement)
}

Escape <- data.frame(Escape)

plot_escape_manipulations <- ggplot(data = Escape, aes(x = Alpha)) +
  geom_line(aes(y = Chinook), color = "seagreen", lwd = 1.2) + 
  geom_line(aes(y = Coho), color = "goldenrod", lwd = 1.2) + 
  geom_line(aes(y = Sockeye), color = "salmon", lwd = 1.2) +
  geom_vline(xintercept = 0.05, lwd = 2, color = "gray", linetype = 2) +
  labs(y = "Salmon Escaped", x = "Alpha (Search and Capture") +
  theme_classic()
plot_escape_manipulations

escape_4_tab <- rbind(Escape[1,], Escape[nrow(Escape),])
escape_4_tab <- escape_4_tab %>% rename_at("Alpha", ~ "Run")
escapement_table <- rbind(base_salmon_escapement, escape_4_tab)

kable(escapement_table, caption = "Escaped Salmon") %>% kable_styling(full_width = F, font_size = font_size)
```

## Cmax

```{r Cmax, message = FALSE, echo = FALSE, warning = FALSE, fig.height=fig.height, fig.width = fig.width}

source("Ballard/02_Prep_Ballard_salmon_data.R")
source("Ballard/03_set_pars.R")

Cmax_list <- seq(1, 15, 3)

Escape <- data.frame(Cmax = 0, Sockeye = NA, Chinook = NA, Coho = NA)
for(i in 1:length(Cmax_list)){
  Cmax <- Cmax_list[i]
  source("Ballard/04_initialize_variables.R")
  source("Ballard/assembleLegosBallard.R")
  Escape[i,] <- data.frame(Cmax = Cmax, salmon_escapement)
}

Escape <- data.frame(Escape)

plot_escape_manipulations <- ggplot(data = Escape, aes(x = Cmax)) +
  geom_line(aes(y = Chinook), color = "seagreen", lwd = 1.2) + 
  geom_line(aes(y = Coho), color = "goldenrod", lwd = 1.2) + 
  geom_line(aes(y = Sockeye), color = "salmon", lwd = 1.2) +
  geom_vline(xintercept = 5, lwd = 2, color = "gray", linetype = 2) +
  labs(y = "Salmon Escaped", x = "Cmax") +
  theme_classic()
plot_escape_manipulations

escape_4_tab <- rbind(Escape[1,], Escape[nrow(Escape),])
escape_4_tab <- escape_4_tab %>% rename_at("Cmax", ~ "Run")
escapement_table <- rbind(base_salmon_escapement, escape_4_tab)

kable(escapement_table, caption = "Escaped Salmon") %>% kable_styling(full_width = F, font_size = font_size)
```

## Cmax sealions

```{r Cmax sealion, message = FALSE, echo = FALSE, warning = FALSE, fig.height=fig.height, fig.width = fig.width}

source("Ballard/02_Prep_Ballard_salmon_data.R")
source("Ballard/03_set_pars.R")

Cmax_sealion_list <- seq(1, 31, 5)

Escape <- data.frame(Cmax_sealion = 0, Sockeye = NA, Chinook = NA, Coho = NA)
for(i in 1:length(Cmax_sealion_list)){
  Cmax_ej <- Cmax_sealion_list[i]
  Cmax_zc <- Cmax_sealion_list[i]
  source("Ballard/04_initialize_variables.R")
  source("Ballard/assembleLegosBallard.R")
  Escape[i,] <- data.frame(Cmax_sealion = Cmax_ej, salmon_escapement)
}

Escape <- data.frame(Escape)

plot_escape_manipulations <- ggplot(data = Escape, aes(x = Cmax_sealion)) +
  geom_line(aes(y = Chinook), color = "seagreen", lwd = 1.2) + 
  geom_line(aes(y = Coho), color = "goldenrod", lwd = 1.2) + 
  geom_line(aes(y = Sockeye), color = "salmon", lwd = 1.2) +
  geom_vline(xintercept = 20, lwd = 2, color = "gray", linetype = 2) +
  labs(y = "Salmon Escaped", x = "Cmax_sealion") +
  theme_classic()
plot_escape_manipulations

escape_4_tab <- rbind(Escape[1,], Escape[nrow(Escape),])
escape_4_tab <- escape_4_tab %>% rename_at("Cmax_sealion", ~ "Run")
escapement_table <- rbind(base_salmon_escapement, escape_4_tab)

kable(escapement_table, caption = "Escaped Salmon") %>% kable_styling(full_width = F, font_size = font_size)
```

## gamma

```{r gamma, message = FALSE, echo = FALSE, warning = FALSE, fig.height=fig.height, fig.width = fig.width}

source("Ballard/02_Prep_Ballard_salmon_data.R")
source("Ballard/03_set_pars.R")

gamma_list <- seq(-1, 0, 0.2)

Escape <- data.frame(Gamma = 0, Sockeye = NA, Chinook = NA, Coho = NA)
for(i in 1:length(gamma_list)){
  gamma <- gamma_list[i]
  source("Ballard/04_initialize_variables.R")
  source("Ballard/assembleLegosBallard.R")
  Escape[i,] <- data.frame(Gamma = gamma, salmon_escapement)
}

Escape <- data.frame(Escape)

plot_escape_manipulations <- ggplot(data = Escape, aes(x = Gamma)) +
  geom_line(aes(y = Chinook), color = "seagreen", lwd = 1.2) + 
  geom_line(aes(y = Coho), color = "goldenrod", lwd = 1.2) + 
  geom_line(aes(y = Sockeye), color = "salmon", lwd = 1.2) +
  geom_vline(xintercept = -1, lwd = 2, color = "gray", linetype = 2) +
  labs(y = "Salmon Escaped", x = "gamma") +
  theme_classic()
plot_escape_manipulations

escape_4_tab <- rbind(Escape[1,], Escape[nrow(Escape),])
escape_4_tab <- escape_4_tab %>% rename_at("Gamma", ~ "Run")
escapement_table <- rbind(base_salmon_escapement, escape_4_tab)

kable(escapement_table, caption = "Escaped Salmon") %>% kable_styling(full_width = F, font_size = font_size)
```

## specialist_prob

```{r specialist_prob, message = FALSE, echo = FALSE, warning = FALSE, fig.height=fig.height, fig.width = fig.width}

source("Ballard/02_Prep_Ballard_salmon_data.R")
source("Ballard/03_set_pars.R")

specialist_prob_list <- seq(0, 1, 0.2)

Escape <- data.frame(specialist_prob = 0, Sockeye = NA, Chinook = NA, Coho = NA)
for(i in 1:length(specialist_prob_list)){
  specialist_prob <- specialist_prob_list[i]
  source("Ballard/04_initialize_variables.R")
  source("Ballard/assembleLegosBallard.R")
  Escape[i,] <- data.frame(specialist_prob = specialist_prob, salmon_escapement)
}

Escape <- data.frame(Escape)

plot_escape_manipulations <- ggplot(data = Escape, aes(x = specialist_prob)) +
  geom_line(aes(y = Chinook), color = "seagreen", lwd = 1.2) + 
  geom_line(aes(y = Coho), color = "goldenrod", lwd = 1.2) + 
  geom_line(aes(y = Sockeye), color = "salmon", lwd = 1.2) +
  geom_vline(xintercept = 0.5, lwd = 2, color = "gray", linetype = 2) +
  labs(y = "Salmon Escaped", x = "specialist_prob") +
  theme_classic()
plot_escape_manipulations

escape_4_tab <- rbind(Escape[1,], Escape[nrow(Escape),])
escape_4_tab <- escape_4_tab %>% rename_at("specialist_prob", ~ "Run")
escapement_table <- rbind(base_salmon_escapement, escape_4_tab)

kable(escapement_table, caption = "Escaped Salmon") %>% kable_styling(full_width = F, font_size = font_size)
```


## w (relative goodness of the Gauntlet)

```{r w, message = FALSE, echo = FALSE, warning = FALSE, fig.height=fig.height, fig.width = fig.width}

source("Ballard/02_Prep_Ballard_salmon_data.R")
source("Ballard/03_set_pars.R")

w_list <- seq(0, 10, 2)

Escape <- data.frame(w = 0, Sockeye = NA, Chinook = NA, Coho = NA)
for(i in 1:length(w_list)){
  w <- w_list[i]
  source("Ballard/04_initialize_variables.R")
  source("Ballard/assembleLegosBallard.R")
  Escape[i,] <- data.frame(w = w, salmon_escapement)
}

Escape <- data.frame(Escape)

plot_escape_manipulations <- ggplot(data = Escape, aes(x = w)) +
  geom_line(aes(y = Chinook), color = "seagreen", lwd = 1.2) + 
  geom_line(aes(y = Coho), color = "goldenrod", lwd = 1.2) + 
  geom_line(aes(y = Sockeye), color = "salmon", lwd = 1.2) +
  geom_vline(xintercept = 1, lwd = 2, color = "gray", linetype = 2) +
  labs(y = "Salmon Escaped", x = "w") +
  theme_classic()
plot_escape_manipulations

escape_4_tab <- rbind(Escape[1,], Escape[nrow(Escape),])
escape_4_tab <- escape_4_tab %>% rename_at("w", ~ "Run")
escapement_table <- rbind(base_salmon_escapement, escape_4_tab)

kable(escapement_table, caption = "Escaped Salmon") %>% kable_styling(full_width = F, font_size = font_size)
```


## w (sea lions)

```{r w sealion, message = FALSE, echo = FALSE, warning = FALSE, fig.height=fig.height, fig.width = fig.width}

source("Ballard/02_Prep_Ballard_salmon_data.R")
source("Ballard/03_set_pars.R")

w_sealion_list <- seq(0, 30, 6)

Escape <- data.frame(w_sealion = 0, Sockeye = NA, Chinook = NA, Coho = NA)
for(i in 1:length(w_sealion_list)){
  w_sealion <- w_sealion_list[i]
  source("Ballard/04_initialize_variables.R")
  source("Ballard/assembleLegosBallard.R")
  Escape[i,] <- data.frame(w_sealion = w_sealion, salmon_escapement)
}

Escape <- data.frame(Escape)

plot_escape_manipulations <- ggplot(data = Escape, aes(x = w_sealion)) +
  geom_line(aes(y = Chinook), color = "seagreen", lwd = 1.2) + 
  geom_line(aes(y = Coho), color = "goldenrod", lwd = 1.2) + 
  geom_line(aes(y = Sockeye), color = "salmon", lwd = 1.2) +
  geom_vline(xintercept = 20, lwd = 2, color = "gray", linetype = 2) +
  labs(y = "Salmon Escaped", x = "w sealion") +
  theme_classic()
plot_escape_manipulations

escape_4_tab <- rbind(Escape[1,], Escape[nrow(Escape),])
escape_4_tab <- escape_4_tab %>% rename_at("w_sealion", ~ "Run")
escapement_table <- rbind(base_salmon_escapement, escape_4_tab)

kable(escapement_table, caption = "Escaped Salmon") %>% kable_styling(full_width = F, font_size = font_size)
```

## intercept_x_val

```{r intercept_x_val, message = FALSE, echo = FALSE, warning = FALSE, fig.height=fig.height, fig.width = fig.width}

source("Ballard/02_Prep_Ballard_salmon_data.R")
source("Ballard/03_set_pars.R")

intercept_x_val_list <- seq(0, 0.1, 0.02)

Escape <- data.frame(intercept_x_val = 0, Sockeye = NA, Chinook = NA, Coho = NA)
for(i in 1:length(intercept_x_val_list)){
  intercept_x_val <- intercept_x_val_list[i]
  source("Ballard/04_initialize_variables.R")
  source("Ballard/assembleLegosBallard.R")
  Escape[i,] <- data.frame(intercept_x_val = intercept_x_val, salmon_escapement)
}

Escape <- data.frame(Escape)

plot_escape_manipulations <- ggplot(data = Escape, aes(x = intercept_x_val)) +
  geom_line(aes(y = Chinook), color = "seagreen", lwd = 1.2) + 
  geom_line(aes(y = Coho), color = "goldenrod", lwd = 1.2) + 
  geom_line(aes(y = Sockeye), color = "salmon", lwd = 1.2) +
  geom_vline(xintercept = 0.01, lwd = 2, color = "gray", linetype = 2) +
  labs(y = "Salmon Escaped", x = "intercept_x_val") +
  theme_classic()
plot_escape_manipulations

escape_4_tab <- rbind(Escape[1,], Escape[nrow(Escape),])
escape_4_tab <- escape_4_tab %>% rename_at("intercept_x_val", ~ "Run")
escapement_table <- rbind(base_salmon_escapement, escape_4_tab)

kable(escapement_table, caption = "Escaped Salmon") %>% kable_styling(full_width = F, font_size = font_size)
```

## steepness (y --> Py)

```{r steepness (y), message = FALSE, echo = FALSE, warning = FALSE, fig.height=fig.height, fig.width = fig.width}

source("Ballard/02_Prep_Ballard_salmon_data.R")
source("Ballard/03_set_pars.R")

steepness_list <- seq(0, 2.5, 0.5)

Escape <- data.frame(steepness = 0, Sockeye = NA, Chinook = NA, Coho = NA)
for(i in 1:length(steepness_list)){
  steepness <- steepness_list[i]
  source("Ballard/04_initialize_variables.R")
  source("Ballard/assembleLegosBallard.R")
  Escape[i,] <- data.frame(steepness = steepness, salmon_escapement)
}

Escape <- data.frame(Escape)

plot_escape_manipulations <- ggplot(data = Escape, aes(x = steepness)) +
  geom_line(aes(y = Chinook), color = "seagreen", lwd = 1.2) + 
  geom_line(aes(y = Coho), color = "goldenrod", lwd = 1.2) + 
  geom_line(aes(y = Sockeye), color = "salmon", lwd = 1.2) +
  geom_vline(xintercept = 1, lwd = 2, color = "gray", linetype = 2) +
  labs(y = "Salmon Escaped", x = "steepness (y)") +
  theme_classic()
plot_escape_manipulations

escape_4_tab <- rbind(Escape[1,], Escape[nrow(Escape),])
escape_4_tab <- escape_4_tab %>% rename_at("steepness", ~ "Run")
escapement_table <- rbind(base_salmon_escapement, escape_4_tab)

kable(escapement_table, caption = "Escaped Salmon") %>% kable_styling(full_width = F, font_size = font_size)
```

## threshold_val (y --> Py)

```{r threshold (y), message = FALSE, echo = FALSE, warning = FALSE, fig.height=fig.height, fig.width = fig.width}

source("Ballard/02_Prep_Ballard_salmon_data.R")
source("Ballard/03_set_pars.R")

threshold_val_list <- seq(-10, 0, 2)

Escape <- data.frame(threshold_val = 0, Sockeye = NA, Chinook = NA, Coho = NA)
for(i in 1:length(threshold_val_list)){
  threshold_val <- threshold_val_list[i]
  source("Ballard/04_initialize_variables.R")
  source("Ballard/assembleLegosBallard.R")
  Escape[i,] <- data.frame(threshold_val = threshold_val, salmon_escapement)
}

Escape <- data.frame(Escape)

plot_escape_manipulations <- ggplot(data = Escape, aes(x = threshold_val)) +
  geom_line(aes(y = Chinook), color = "seagreen", lwd = 1.2) + 
  geom_line(aes(y = Coho), color = "goldenrod", lwd = 1.2) + 
  geom_line(aes(y = Sockeye), color = "salmon", lwd = 1.2) +
  geom_vline(xintercept = -5, lwd = 2, color = "gray", linetype = 2) +
  labs(y = "Salmon Escaped", x = "threshold_val") +
  theme_classic()
plot_escape_manipulations

escape_4_tab <- rbind(Escape[1,], Escape[nrow(Escape),])
escape_4_tab <- escape_4_tab %>% rename_at("threshold_val", ~ "Run")
escapement_table <- rbind(base_salmon_escapement, escape_4_tab)

kable(escapement_table, caption = "Escaped Salmon") %>% kable_styling(full_width = F, font_size = font_size)
```

## steepness_x_specialist

```{r steepness_x_specialist, message = FALSE, echo = FALSE, warning = FALSE, fig.height=fig.height, fig.width = fig.width}

source("Ballard/02_Prep_Ballard_salmon_data.R")
source("Ballard/03_set_pars.R")

steepness_x_specialist_list <- seq(0, 3, 0.5)

Escape <- data.frame(steepness_x_specialist = 0, Sockeye = NA, Chinook = NA, Coho = NA)
for(i in 1:length(steepness_x_specialist_list)){
  steepness_x_specialist <- steepness_x_specialist_list[i]
  source("Ballard/04_initialize_variables.R")
  source("Ballard/assembleLegosBallard.R")
  Escape[i,] <- data.frame(steepness_x_specialist = steepness_x_specialist, salmon_escapement)
}

Escape <- data.frame(Escape)

plot_escape_manipulations <- ggplot(data = Escape, aes(x = steepness_x_specialist)) +
  geom_line(aes(y = Chinook), color = "seagreen", lwd = 1.2) + 
  geom_line(aes(y = Coho), color = "goldenrod", lwd = 1.2) + 
  geom_line(aes(y = Sockeye), color = "salmon", lwd = 1.2) +
  geom_vline(xintercept = 0.1, lwd = 2, color = "gray", linetype = 2) +
  labs(y = "Salmon Escaped", x = "steepness_x_specialist") +
  theme_classic()
plot_escape_manipulations

escape_4_tab <- rbind(Escape[1,], Escape[nrow(Escape),])
escape_4_tab <- escape_4_tab %>% rename_at("steepness_x_specialist", ~ "Run")
escapement_table <- rbind(base_salmon_escapement, escape_4_tab)

kable(escapement_table, caption = "Escaped Salmon") %>% kable_styling(full_width = F, font_size = font_size)
```

## threshold_x_specialist

```{r threshold_x_specialist, message = FALSE, echo = FALSE, warning = FALSE, fig.height=fig.height, fig.width = fig.width}

source("Ballard/02_Prep_Ballard_salmon_data.R")
source("Ballard/03_set_pars.R")

threshold_x_specialist_list <- seq(0, 10, 2)

Escape <- data.frame(threshold_x_specialist = 0, Sockeye = NA, Chinook = NA, Coho = NA)
for(i in 1:length(threshold_x_specialist_list)){
  threshold_x_specialist <- threshold_x_specialist_list[i]
  source("Ballard/04_initialize_variables.R")
  source("Ballard/assembleLegosBallard.R")
  Escape[i,] <- data.frame(threshold_x_specialist = threshold_x_specialist, salmon_escapement)
}

Escape <- data.frame(Escape)

plot_escape_manipulations <- ggplot(data = Escape, aes(x = threshold_x_specialist)) +
  geom_line(aes(y = Chinook), color = "seagreen", lwd = 1.2) + 
  geom_line(aes(y = Coho), color = "goldenrod", lwd = 1.2) + 
  geom_line(aes(y = Sockeye), color = "salmon", lwd = 1.2) +
  geom_vline(xintercept = 0.1, lwd = 2, color = "gray", linetype = 2) +
  labs(y = "Salmon Escaped", x = "threshold_x_specialist") +
  theme_classic()
plot_escape_manipulations

escape_4_tab <- rbind(Escape[1,], Escape[nrow(Escape),])
escape_4_tab <- escape_4_tab %>% rename_at("threshold_x_specialist", ~ "Run")
escapement_table <- rbind(base_salmon_escapement, escape_4_tab)

kable(escapement_table, caption = "Escaped Salmon") %>% kable_styling(full_width = F, font_size = font_size)
```


## step

```{r step, message = FALSE, echo = FALSE, warning = FALSE, fig.height=fig.height, fig.width = fig.width}

source("Ballard/02_Prep_Ballard_salmon_data.R")
source("Ballard/03_set_pars.R")

step_list <- seq(0, 2, 0.5)

Escape <- data.frame(step = 0, Sockeye = NA, Chinook = NA, Coho = NA)
for(i in 1:length(step_list)){
  step <- step_list[i]
  source("Ballard/04_initialize_variables.R")
  source("Ballard/assembleLegosBallard.R")
  Escape[i,] <- data.frame(step = step, salmon_escapement)
}

Escape <- data.frame(Escape)

plot_escape_manipulations <- ggplot(data = Escape, aes(x = step)) +
  geom_line(aes(y = Chinook), color = "seagreen", lwd = 1.2) + 
  geom_line(aes(y = Coho), color = "goldenrod", lwd = 1.2) + 
  geom_line(aes(y = Sockeye), color = "salmon", lwd = 1.2) +
  geom_vline(xintercept = 0.5, lwd = 2, color = "gray", linetype = 2) +
  labs(y = "Salmon Escaped", x = "step") +
  theme_classic()
plot_escape_manipulations

escape_4_tab <- rbind(Escape[1,], Escape[nrow(Escape),])
escape_4_tab <- escape_4_tab %>% rename_at("step", ~ "Run")
escapement_table <- rbind(base_salmon_escapement, escape_4_tab)

kable(escapement_table, caption = "Escaped Salmon") %>% kable_styling(full_width = F, font_size = font_size)
```


## decay

```{r decay, message = FALSE, echo = FALSE, warning = FALSE, fig.height=fig.height, fig.width = fig.width}

source("Ballard/02_Prep_Ballard_salmon_data.R")
source("Ballard/03_set_pars.R")

decay_list <- seq(0, 2, 0.25)

Escape <- data.frame(decay = 0, Sockeye = NA, Chinook = NA, Coho = NA)
for(i in 1:length(decay_list)){
  decay <- decay_list[i]
  source("Ballard/04_initialize_variables.R")
  source("Ballard/assembleLegosBallard.R")
  Escape[i,] <- data.frame(decay = decay, salmon_escapement)
}

Escape <- data.frame(Escape)

plot_escape_manipulations <- ggplot(data = Escape, aes(x = decay)) +
  geom_line(aes(y = Chinook), color = "seagreen", lwd = 1.2) + 
  geom_line(aes(y = Coho), color = "goldenrod", lwd = 1.2) + 
  geom_line(aes(y = Sockeye), color = "salmon", lwd = 1.2) +
  geom_vline(xintercept = 0.5, lwd = 2, color = "gray", linetype = 2) +
  labs(y = "Salmon Escaped", x = "decay") +
  theme_classic()
plot_escape_manipulations

escape_4_tab <- rbind(Escape[1,], Escape[nrow(Escape),])
escape_4_tab <- escape_4_tab %>% rename_at("decay", ~ "Run")
escapement_table <- rbind(base_salmon_escapement, escape_4_tab)

kable(escapement_table, caption = "Escaped Salmon") %>% kable_styling(full_width = F, font_size = font_size)
```

## num_seals_2_copy

```{r num_seals_2_copy, message = FALSE, echo = FALSE, warning = FALSE, fig.height=fig.height, fig.width = fig.width}

source("Ballard/02_Prep_Ballard_salmon_data.R")
source("Ballard/03_set_pars.R")

num_seals_2_copy_list <- seq(0, num_seals, 15)

Escape <- data.frame(num_seals_2_copy = 0, Sockeye = NA, Chinook = NA, Coho = NA)
for(i in 1:length(num_seals_2_copy_list)){
  num_seals_2_copy <- num_seals_2_copy_list[i]
  source("Ballard/04_initialize_variables.R")
  source("Ballard/assembleLegosBallard.R")
  Escape[i,] <- data.frame(num_seals_2_copy = num_seals_2_copy, salmon_escapement)
}

Escape <- data.frame(Escape)

plot_escape_manipulations <- ggplot(data = Escape, aes(x = num_seals_2_copy)) +
  geom_line(aes(y = Chinook), color = "seagreen", lwd = 1.2) + 
  geom_line(aes(y = Coho), color = "goldenrod", lwd = 1.2) + 
  geom_line(aes(y = Sockeye), color = "salmon", lwd = 1.2) +
  geom_vline(xintercept = 0, lwd = 2, color = "gray", linetype = 2) +
  labs(y = "Salmon Escaped", x = "num_seals_2_copy") +
  theme_classic()
plot_escape_manipulations

escape_4_tab <- rbind(Escape[1,], Escape[nrow(Escape),])
escape_4_tab <- escape_4_tab %>% rename_at("num_seals_2_copy", ~ "Run")
escapement_table <- rbind(base_salmon_escapement, escape_4_tab)

kable(escapement_table, caption = "Escaped Salmon") %>% kable_styling(full_width = F, font_size = font_size)
```


## beta (receptivity spread)

```{r beta, message = FALSE, echo = FALSE, warning = FALSE, fig.height=fig.height, fig.width = fig.width}

source("Ballard/02_Prep_Ballard_salmon_data.R")
source("Ballard/03_set_pars.R")

beta_list <- seq(0, 50, 10)

Escape <- data.frame(beta = 0, Sockeye = NA, Chinook = NA, Coho = NA)
for(i in 1:length(beta_list)){
  beta <- beta_list[i]
  source("Ballard/04_initialize_variables.R")
  source("Ballard/assembleLegosBallard.R")
  Escape[i,] <- data.frame(beta = beta, salmon_escapement)
}

Escape <- data.frame(Escape)

plot_escape_manipulations <- ggplot(data = Escape, aes(x = beta)) +
  geom_line(aes(y = Chinook), color = "seagreen", lwd = 1.2) + 
  geom_line(aes(y = Coho), color = "goldenrod", lwd = 1.2) + 
  geom_line(aes(y = Sockeye), color = "salmon", lwd = 1.2) +
  geom_vline(xintercept = 15, lwd = 2, color = "gray", linetype = 2) +
  labs(y = "Salmon Escaped", x = "beta (spread)") +
  theme_classic()
plot_escape_manipulations

escape_4_tab <- rbind(Escape[1,], Escape[nrow(Escape),])
escape_4_tab <- escape_4_tab %>% rename_at("beta", ~ "Run")
escapement_table <- rbind(base_salmon_escapement, escape_4_tab)

kable(escapement_table, caption = "Escaped Salmon") %>% kable_styling(full_width = F, font_size = font_size)
```


## sockeye_escape_rate

```{r sockeye_escape_rate, message = FALSE, echo = FALSE, warning = FALSE, fig.height=fig.height, fig.width = fig.width}

source("Ballard/02_Prep_Ballard_salmon_data.R")
source("Ballard/03_set_pars.R")

sockeye_escape_rate_list <- seq(0, 0.5, 0.01)

Escape <- data.frame(sockeye_escape_rate = 0, Sockeye = NA, Chinook = NA, Coho = NA)
for(i in 1:length(sockeye_escape_rate_list)){
  sockeye_escape_rate <- sockeye_escape_rate_list[i]
  source("Ballard/04_initialize_variables.R")
  source("Ballard/assembleLegosBallard.R")
  Escape[i,] <- data.frame(sockeye_escape_rate = sockeye_escape_rate, salmon_escapement)
}

Escape <- data.frame(Escape)

plot_escape_manipulations <- ggplot(data = Escape, aes(x = sockeye_escape_rate)) +
  geom_line(aes(y = Chinook), color = "seagreen", lwd = 1.2) + 
  geom_line(aes(y = Coho), color = "goldenrod", lwd = 1.2) + 
  geom_line(aes(y = Sockeye), color = "salmon", lwd = 1.2) +
  geom_vline(xintercept = 0.3, lwd = 2, color = "gray", linetype = 2) +
  labs(y = "Salmon Escaped", x = "sockeye_escape_rate") +
  theme_classic()
plot_escape_manipulations

escape_4_tab <- rbind(Escape[1,], Escape[nrow(Escape),])
escape_4_tab <- escape_4_tab %>% rename_at("sockeye_escape_rate", ~ "Run")
escapement_table <- rbind(base_salmon_escapement, escape_4_tab)

kable(escapement_table, caption = "Escaped Salmon") %>% kable_styling(full_width = F, font_size = font_size)
```

## chinook_escape_rate

```{r chinook_escape_rate, message = FALSE, echo = FALSE, warning = FALSE, fig.height=fig.height, fig.width = fig.width}

source("Ballard/02_Prep_Ballard_salmon_data.R")
source("Ballard/03_set_pars.R")

chinook_escape_rate_list <- seq(0, 0.3, 0.05)

Escape <- data.frame(chinook_escape_rate = 0, Sockeye = NA, Chinook = NA, Coho = NA)
for(i in 1:length(chinook_escape_rate_list)){
  chinook_escape_rate <- chinook_escape_rate_list[i]
  source("Ballard/04_initialize_variables.R")
  source("Ballard/assembleLegosBallard.R")
  Escape[i,] <- data.frame(chinook_escape_rate = chinook_escape_rate, salmon_escapement)
}

Escape <- data.frame(Escape)

plot_escape_manipulations <- ggplot(data = Escape, aes(x = chinook_escape_rate)) +
  geom_line(aes(y = Chinook), color = "seagreen", lwd = 1.2) + 
  geom_line(aes(y = Coho), color = "goldenrod", lwd = 1.2) + 
  geom_line(aes(y = Sockeye), color = "salmon", lwd = 1.2) +
  geom_vline(xintercept = 0.015, lwd = 2, color = "gray", linetype = 2) +
  labs(y = "Salmon Escaped", x = "chinook_escape_rate") +
  theme_classic()
plot_escape_manipulations

escape_4_tab <- rbind(Escape[1,], Escape[nrow(Escape),])
escape_4_tab <- escape_4_tab %>% rename_at("chinook_escape_rate", ~ "Run")
escapement_table <- rbind(base_salmon_escapement, escape_4_tab)

kable(escapement_table, caption = "Escaped Salmon") %>% kable_styling(full_width = F, font_size = font_size)
```

## coho_escape_rate

```{r coho_escape_rate, message = FALSE, echo = FALSE, warning = FALSE, fig.height=fig.height, fig.width = fig.width}

source("Ballard/02_Prep_Ballard_salmon_data.R")
source("Ballard/03_set_pars.R")

coho_escape_rate_list <- seq(0, 0.5, 0.1)

Escape <- data.frame(coho_escape_rate = 0, Sockeye = NA, Chinook = NA, Coho = NA)
for(i in 1:length(coho_escape_rate_list)){
  coho_escape_rate <- coho_escape_rate_list[i]
  source("Ballard/04_initialize_variables.R")
  source("Ballard/assembleLegosBallard.R")
  Escape[i,] <- data.frame(coho_escape_rate = coho_escape_rate, salmon_escapement)
}

Escape <- data.frame(Escape)

plot_escape_manipulations <- ggplot(data = Escape, aes(x = coho_escape_rate)) +
  geom_line(aes(y = Chinook), color = "seagreen", lwd = 1.2) + 
  geom_line(aes(y = Coho), color = "goldenrod", lwd = 1.2) + 
  geom_line(aes(y = Sockeye), color = "salmon", lwd = 1.2) +
  geom_vline(xintercept = 0.1, lwd = 2, color = "gray", linetype = 2) +
  labs(y = "Salmon Escaped", x = "coho_escape_rate") +
  theme_classic()
plot_escape_manipulations

escape_4_tab <- rbind(Escape[1,], Escape[nrow(Escape),])
escape_4_tab <- escape_4_tab %>% rename_at("coho_escape_rate", ~ "Run")
escapement_table <- rbind(base_salmon_escapement, escape_4_tab)

kable(escapement_table, caption = "Escaped Salmon") %>% kable_styling(full_width = F, font_size = font_size)
```

## natural_mort

```{r natural_mort, message = FALSE, echo = FALSE, warning = FALSE, fig.height=fig.height, fig.width = fig.width}

source("Ballard/02_Prep_Ballard_salmon_data.R")
source("Ballard/03_set_pars.R")

natural_mort_list <- seq(0, 0.001, 0.00025)

Escape <- data.frame(natural_mort = 0, Sockeye = NA, Chinook = NA, Coho = NA)
for(i in 1:length(natural_mort_list)){
  natural_mort <- natural_mort_list[i]
  source("Ballard/04_initialize_variables.R")
  source("Ballard/assembleLegosBallard.R")
  Escape[i,] <- data.frame(natural_mort = natural_mort, salmon_escapement)
}

Escape <- data.frame(Escape)

plot_escape_manipulations <- ggplot(data = Escape, aes(x = natural_mort)) +
  geom_line(aes(y = Chinook), color = "seagreen", lwd = 1.2) + 
  geom_line(aes(y = Coho), color = "goldenrod", lwd = 1.2) + 
  geom_line(aes(y = Sockeye), color = "salmon", lwd = 1.2) +
  geom_vline(xintercept = 0.0005, lwd = 2, color = "gray", linetype = 2) +
  labs(y = "Salmon Escaped", x = "natural_mort") +
  theme_classic()
plot_escape_manipulations

escape_4_tab <- rbind(Escape[1,], Escape[nrow(Escape),])
escape_4_tab <- escape_4_tab %>% rename_at("natural_mort", ~ "Run")
escapement_table <- rbind(base_salmon_escapement, escape_4_tab)

kable(escapement_table, caption = "Escaped Salmon") %>% kable_styling(full_width = F, font_size = font_size)
```

## steepness_H

```{r steepness_H, message = FALSE, echo = FALSE, warning = FALSE, fig.height=fig.height, fig.width = fig.width}

source("Ballard/02_Prep_Ballard_salmon_data.R")
source("Ballard/03_set_pars.R")

steepness_H_list <- seq(0, 200, 50)

Escape <- data.frame(steepness_H = 0, Sockeye = NA, Chinook = NA, Coho = NA)
for(i in 1:length(steepness_H_list)){
  steepness_H <- steepness_H_list[i]
  source("Ballard/04_initialize_variables.R")
  source("Ballard/assembleLegosBallard.R")
  Escape[i,] <- data.frame(steepness_H = steepness_H, salmon_escapement)
}

Escape <- data.frame(Escape)

plot_escape_manipulations <- ggplot(data = Escape, aes(x = steepness_H)) +
  geom_line(aes(y = Chinook), color = "seagreen", lwd = 1.2) + 
  geom_line(aes(y = Coho), color = "goldenrod", lwd = 1.2) + 
  geom_line(aes(y = Sockeye), color = "salmon", lwd = 1.2) +
  geom_vline(xintercept = 10, lwd = 2, color = "gray", linetype = 2) +
  labs(y = "Salmon Escaped", x = "steepness_H") +
  theme_classic()
plot_escape_manipulations

escape_4_tab <- rbind(Escape[1,], Escape[nrow(Escape),])
escape_4_tab <- escape_4_tab %>% rename_at("steepness_H", ~ "Run")
escapement_table <- rbind(base_salmon_escapement, escape_4_tab)

kable(escapement_table, caption = "Escaped Salmon") %>% kable_styling(full_width = F, font_size = font_size)
```


## efficiency

```{r efficiency, message = FALSE, echo = FALSE, warning = FALSE, fig.height=fig.height, fig.width = fig.width}

source("Ballard/02_Prep_Ballard_salmon_data.R")
source("Ballard/03_set_pars.R")

efficiency_list <- seq(0, 0.5, 0.1)

Escape <- data.frame(efficiency = 0, Sockeye = NA, Chinook = NA, Coho = NA)
for(i in 1:length(efficiency_list)){
  efficiency <- efficiency_list[i]
  source("Ballard/04_initialize_variables.R")
  source("Ballard/assembleLegosBallard.R")
  Escape[i,] <- data.frame(efficiency = efficiency, salmon_escapement)
}

Escape <- data.frame(Escape)

plot_escape_manipulations <- ggplot(data = Escape, aes(x = efficiency)) +
  geom_line(aes(y = Chinook), color = "seagreen", lwd = 1.2) + 
  geom_line(aes(y = Coho), color = "goldenrod", lwd = 1.2) + 
  geom_line(aes(y = Sockeye), color = "salmon", lwd = 1.2) +
  geom_vline(xintercept = 0.075, lwd = 2, color = "gray", linetype = 2) +
  labs(y = "Salmon Escaped", x = "efficiency") +
  theme_classic()
plot_escape_manipulations

escape_4_tab <- rbind(Escape[1,], Escape[nrow(Escape),])
escape_4_tab <- escape_4_tab %>% rename_at("efficiency", ~ "Run")
escapement_table <- rbind(base_salmon_escapement, escape_4_tab)

kable(escapement_table, caption = "Escaped Salmon") %>% kable_styling(full_width = F, font_size = font_size)
```














