---
title: "Experiment: Exclusion Zone Implementation @ Ballard"
subtitle: "Describing the model run when an exclusion zone management strategy is implemented at Ballard"
date: "`r format(Sys.time(), '%B %d, %Y')`"
---

### The Narrative

This Model Run is for a scenario where managers in the Gauntlet enact an "Exclusion Zone" management strategy. In this strategy, all pinnipeds that cross into the Gauntlet area when salmon are present in the Gauntlet are targeted for removal. We assume that managers are able to effectively remove a percentage of pinnipeds in the area that is dependent on the total density of pinnipeds.

### Run the Model

```{r, setup, include = FALSE}
library(knitr)
library(flextable)
library(kableExtra)
knitr::opts_knit$set(root.dir = '~/GitHub/PinnipedCaseStudies')
```

```{r setup the model, include = FALSE, message = FALSE, warning = FALSE}

# 01 Set-Up Functions
source("Functions/01_predictFish.R")
source("Functions/makeArray.R")
source("Functions/createHarvestPlan.R")

# 02 Prep Data
source("Ballard/02_Prep_Ballard_salmon_data.R")

# 03 Set Pars
source("Ballard/03_set_pars.R")
```

```{r set pars, message = FALSE, warning = FALSE}
zone_efficiency <- 0.8
zone_steepness <- 10
scenario <- "Zone"
scenario_sealion <- "Zone"
harvest_open <- start_loop
harvest_close <- end_loop
```

```{r run the loop, include = FALSE, echo = FALSE, warning = FALSE, message = FALSE}
# 04 Initialize Variables
source("Ballard/04_initialize_variables.R")

# 05 Loop Functions
source("Ballard/05_salmonSpeciesUpdate.R")
source("Functions/decideForagingDestination.R")
source("Functions/collusion.R")
source("Functions/rungeKutta_3.R")
source("Functions/getHarvested.R")
source("Functions/learnX.R")
source("Functions/learnY.R")
source("Functions/type3FuncRes.R")
source("Functions/linearFuncRes.R")
source("Functions/updateLearning.R")

# 06 Run The Loop
source("Ballard/06_The_Loop.R")

# 07 Plots
source("Functions/makePlots.R")
source("Functions/Plots_Pv.R")
source("Functions/Plots_Ej.R")
source("Functions/Plots_Zc.R")
source("Ballard/07_Plots_salmon.R")
source("Functions/Plots_responses.R")
```

### Description of Parameterization

This scenario is focused on the effects of implementing an Exclusion Zone management strategy in the Ballard Locks. Under this strategy, both seals and sea lions are removed from the Gauntlet by managers throughout all days of the model run. The proportion of pinnipeds that are removed is governed by an efficiency term which describes the asymptote of the type II response between the number of pinnipeds at the Gauntlet and the proportion of individuals removed. That response is shown below:

```{r efficiency plot, echo = FALSE, warning = FALSE, message = FALSE}
num_pinns <- 0:sum(num_seals, num_ej, num_zc)
plot(num_pinns, zone_efficiency * num_pinns/(steepness + num_pinns), ylab = "Proportion of Pinnipeds Harvested", xlab = "Num Pinnipeds @ Gauntlet")
```

In this parameterization, many more pinnipeds are removed from the system than under incidental or boat-based take only. 

```{r harvest table, echo = FALSE}
kable(data.frame(Pv = sum(H), Ej = sum(H_ej), Zc = sum(H_zc)), caption = "Pinnipeds Removed") %>% kable_styling(full_width = F)
```

```{r pinniped harvest plot, echo = FALSE}
plot_H + plot_H_ej + plot_H_zc
```

Because of the increased removals, this scenario has an impact on pinniped behavior, presence at the Gauntlet, and survival. 

```{r pinnipeds at gauntlet, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 9}
plot_seals + plot_zc + plot_ej + plot_layout(guides = "collect", axes = "collect")
```

In the below plots, you can see the impact of removals on the learning process of individual harbor seals in the decline of the Gauntlet Probabilities.

```{r eaten to probs plots, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 9}
plot_H/plot_y/plot_probs + plot_layout(guides = "collect", axes = "collect")
```

### Things to Note

The total escaped Sockeye, Chinook, and Coho are as follows under this parameterization:

```{r, echo = FALSE}
kable(salmon_escapement) %>% kable_styling(full_width = F)
```

### Parameter Table

```{r, echo = FALSE, message = FALSE, warning = FALSE}
parameters <- data.frame(rbind(days, num_seals, num_zc, num_ej, zone_efficiency, zone_steepness, num_seals_2_copy, sockeye_escape_rate, chinook_escape_rate, coho_escape_rate, Cmax, Cmax_zc, Cmax_ej, alpha))
colnames(parameters) <- c("Value")
kable(parameters) %>% kable_styling(full_width = F)
```
