---
title: "Comparing Management Scenario Model Runs"
subtitle: "Nisqually River Case Study"
date: "`r format(Sys.time(), '%B %d, %Y')`"
---

```{r setup, include = FALSE}

# colors credit to https://github.com/jakelawlor/PNWColors
library(PNWColors)
scenario.colors <- pnw_palette("Sailboat", 6)[c(1,2,3,5)]
```

```{r load scenarios, include = FALSE}
source("Nisqually/Manipulations/Run_BaseRun_Nis.R")
source("Nisqually/Manipulations/Run_BoatHarvest_Nis.R")
source("Nisqually/Manipulations/Run_Zone_Nis.R")
source("Nisqually/Manipulations/Run_Haulout_Nis.R")
```

## Purpose

The purpose of this document is to create figures that enable direct comparison between management scenario model runs, explanation of differences, and interpretation of what that means for the system. 

## Description of the Management Scenarios

In the Nisqually River case study we ran four scenarios:  
####*Base Run*  
Simulates current dynamics in the Gauntlet.  
####*Boat Harvest*  
Simulates amplified harvest by fishers during fishing operations and normal fishing seasons. Alters values for the steepness and efficiency parameters that describe the relationship between the number of fishers and the number of pinnipeds that are harvested.  
####*Zone Exclusion*  
Simulates removals by managers to attempt to exclude all pinnipeds from the Gauntlet. Assumes that no fisher harvest is occuring simulataneously. Alters the process of removals from boat-based to a "zone" scenario that is governed by an efficiency which describes how many of the pinnipeds at that Gauntlet managers can effectively remove (despite aiming for 100% removal).  
####*Haulout Reduction*  
Simulates removals or disturbance by managers to reduce overall pinnipeds in the source pool. Reduces the total number of pinnipeds by a reduction parameter. 


```{r parameter table, echo = FALSE}
parameter_table <- data.frame(Base = base_parameters, Boat = boat_parameters, Zone = zone_parameters, Haulout = haulout_parameters)
colnames(parameter_table) <- c("Base", "Boat", "Zone", "Haulout")
kable(parameter_table, caption = "Parameter Table") %>% kable_styling(full_width = F)
```

## Salmon Response

The total daily salmon presence at the Gauntlet follows two main peaks for the Chinook run and the Chum run. 

```{r gauntlet salmon plot, echo = FALSE, warning = FALSE}

salmon_theme <- theme_classic()

#salmon at gauntlet by species
gauntlet_salmon_sp <- data.frame(Day = (base_salmon_vars[,"Day"] + (start_loop-1)),
                          Base_chum = base_salmon_vars[,"Gauntlet_Chum"],
                          Boat_chum = boat_salmon_vars[,"Gauntlet_Chum"],
                          Zone_chum = zone_salmon_vars[,"Gauntlet_Chum"], 
                          Haulout_chum = haulout_salmon_vars[,"Gauntlet_Chum"],
                          Base_GR = base_salmon_vars[,"Gauntlet_GR"],
                          Boat_GR = boat_salmon_vars[,"Gauntlet_GR"],
                          Zone_GR = zone_salmon_vars[,"Gauntlet_GR"], 
                          Haulout_GR = haulout_salmon_vars[,"Gauntlet_GR"],
                          Base_LN = base_salmon_vars[,"Gauntlet_LN"],
                          Boat_LN = boat_salmon_vars[,"Gauntlet_LN"],
                          Zone_LN = zone_salmon_vars[,"Gauntlet_LN"], 
                          Haulout_LN = haulout_salmon_vars[,"Gauntlet_LN"])

long_gauntlet_salmon_sp <- pivot_longer(round(gauntlet_salmon_sp), cols = "Base_chum":"Haulout_LN",
                                 names_to = "Scenario_temp", values_to = "Gauntlet_salmon")
long_gauntlet_salmon_sp$Species <- rep(rep(c("Chum", "Chinook_GR", "Chinook_LN"), each = 4), times = days)
long_gauntlet_salmon_sp$Scenario <- rep(c("Base", "Boat", "Zone", "Haulout"), times = days*3)

# ggplot(data = long_gauntlet_salmon_sp) +
#   geom_point(aes(x = Day, y = Gauntlet_salmon, color = Scenario)) + 
#   labs(x = "Day of the Year", y = "Salmon at the Gauntlet") +
#   scale_color_manual(values = scenario.colors) + 
#   salmon_theme

# total salmon at gauntlet
gauntlet_salmon_total <- data.frame(Day = (base_salmon_vars[,"Day"] + (start_loop-1)),
                          Base = base_salmon_vars[,"Gauntlet_salmon"],
                          Boat = boat_salmon_vars[,"Gauntlet_salmon"],
                          Zone = zone_salmon_vars[,"Gauntlet_salmon"], 
                          Haulout = haulout_salmon_vars[,"Gauntlet_salmon"])
long_gauntlet_salmon <- pivot_longer(round(gauntlet_salmon_total), cols = "Base":"Haulout",
                                 names_to = "Scenario", values_to = "Gauntlet_salmon")

ggplot(data = long_gauntlet_salmon) +
  geom_point(aes(x = Day, y = Gauntlet_salmon, color = Scenario)) + 
  labs(x = "Day of the Year", y = "Total Salmon at the Gauntlet") +
  scale_color_manual(values = scenario.colors) + 
  salmon_theme
```

The number of salmon that escape the Gauntlet is dependent on their survival from fishing and predation pressures. The following table describes the escapement for each run under each scenario.

```{r escapement table, echo = FALSE}
compare_escape <- data.frame(round(rbind(base_salmon["Escape",], boat_salmon["Escape",],
                                   zone_salmon["Escape",], haulout_salmon["Escape",])))
rownames(compare_escape) <- c("Base", "Boat", "Zone", "Haulout")
kable(compare_escape, caption = "Escapement") %>% kable_styling(full_width = F)
```

Overall, the boat-based harvest and zone management scenarios had the largest improvement in escapement for Chum, but the differences were less pronounced for the two Chinook runs. This mirrors the differences in predation between scenario runs.

```{r consumed salmon table, echo = FALSE}
compare_eaten <- data.frame(round(rbind(base_salmon["Eaten",], boat_salmon["Eaten",],
                                   zone_salmon["Eaten",], haulout_salmon["Eaten",])))
rownames(compare_eaten) <- c("Base", "Boat", "Zone", "Haulout")
kable(compare_eaten, caption = "Predated by Pinnipeds") %>% kable_styling(full_width = F)
```

```{r consumed salmon plot, echo = FALSE}
eaten_salmon_total <- data.frame(Day = (base_salmon_vars[,"Day"] + (start_loop-1)),
                          Base = base_salmon_vars[,"Eaten_salmon"],
                          Boat = boat_salmon_vars[,"Eaten_salmon"],
                          Zone = zone_salmon_vars[,"Eaten_salmon"], 
                          Haulout = haulout_salmon_vars[,"Eaten_salmon"])
long_eaten_salmon_total <- pivot_longer(round(eaten_salmon_total), cols = "Base":"Haulout",
                                 names_to = "Scenario", values_to = "Eaten_salmon")

ggplot(data = long_eaten_salmon_total) +
  geom_point(aes(x = Day, y = Eaten_salmon, color = Scenario)) + 
  labs(x = "Day of the Year", y = "Total Salmon Predation at the Gauntlet") +
  scale_color_manual(values = scenario.colors) + 
  salmon_theme
```


## Pinniped Response

### Pinniped Presence

During the Chinook and Coho fisheries, we model a set number of fishers as an average since participation seems to be pretty consistent. For the Chum fishery, participation is much less consistent (not all days of the fishery have active fishing effort, and days that do have active fishing effort have a wide range of the number of fishers participating) so we model the number of fishers using a random draw, which results in a much wider spread of participation. When fisheries are not open, there is no fishing activity in the Gauntlet, and therefore no boat-based take. Harbor seals particularly respond to this by increasing their presence and predation impact.

```{r pinniped plot theme, include = FALSE}

pinniped_theme <- theme_classic()
```

```{r harvesters plot, echo = FALSE, warning = FALSE, message = FALSE}

ggplot(data = Daily_Fish) + 
  geom_point(aes(x = DayofYear, y = harvesters)) + 
  labs(x = "Day of the Year", y = "Number of Fishers in the Gauntlet") +
  pinniped_theme

```

the following plot shows the number of each species that are removed from the Gauntlet daily under the boat-based and zone management scenarios.

```{r H plots, echo = FALSE, warning = FALSE, message = FALSE}
# harbor seal presence
H_pv <- data.frame(Day = (base_pinniped_vars[,"Day"] + (start_loop-1)),
                          Base = base_pinniped_vars[,"H_Pv"],
                          Boat = boat_pinniped_vars[,"H_Pv"],
                          Zone = zone_pinniped_vars[,"H_Pv"], 
                          Haulout = haulout_pinniped_vars[,"H_Pv"])

long_H_pv <- pivot_longer(H_pv, cols = "Base":"Haulout",
                                 names_to = "Scenario", values_to = "H_Pv")
set.seed(5)
ggplot(data = long_H_pv) +
  geom_point(aes(x = Day, y = H_Pv, color = Scenario), size = 2, position = position_jitter()) + 
  labs(x = "Day of the Year", y = "Harbor Seals Harvested per Day") +
  scale_color_manual(values = scenario.colors) + 
  pinniped_theme
```

The following plots describe pinniped presence at the Gauntlet under all four scenarios for each pinniped species separately. You can see that the magnitude of presence differs greatly between scenarios. In the base scenario and haulout reduction scenario, removals aren't happening in the Gauntlet so pinniped presence closely tracks the timing of each salmon run. In the zone management scenario, pinniped presence is low throughout the model run due to the constant fear conditioning from daily removal activity. In the boat-based harvest scenario, you can see that harbor seal presence closely mirrors the presence of fishers in the Gauntlet, only increasing when fishers are not active.

```{r gauntlet seals plots, echo = FALSE, warning = FALSE, message = FALSE}
# harbor seal presence
gauntlet_pv <- data.frame(Day = (base_pinniped_vars[,"Day"] + (start_loop-1)),
                          Base = base_pinniped_vars[,"Gauntlet_Pv"],
                          Boat = boat_pinniped_vars[,"Gauntlet_Pv"],
                          Zone = zone_pinniped_vars[,"Gauntlet_Pv"], 
                          Haulout = haulout_pinniped_vars[,"Gauntlet_Pv"])

long_gauntlet_pv <- pivot_longer(gauntlet_pv, cols = "Base":"Haulout",
                                 names_to = "Scenario", values_to = "Gauntlet_Pv")

ggplot(data = long_gauntlet_pv) +
  geom_line(aes(x = Day, y = Gauntlet_Pv, color = Scenario), lwd = 1) + 
  labs(x = "Day of the Year", y = "Harbor Seals at the Gauntlet") +
  scale_color_manual(values = scenario.colors) + 
  pinniped_theme
```

Sea lions arrive at Nisqually on the `r sealion_arrival_date`th day of the year. Their presence at the Gauntlet is initially high when they first arrive at the tail end of the Chinook runs, then stays low until the Chum run begins to pick up. Their presence is heavily impacted by the management actions, with much smaller presence under the boat-based harvest or zone management scenarios, and moderate reductions under the haulout scenario. Because sea lions are assumed to be more responsive to the resource availability (Chum salmon), they all act like specialists and are all likely to choose the Gauntlet every day unless deterrent actions are taken.

```{r gauntlet sea lions plots, echo = FALSE, warning = FALSE, message = FALSE}
# california presence
gauntlet_zc <- data.frame(Day = (base_pinniped_vars[,"Day"] + (start_loop-1)),
                          Base = base_pinniped_vars[,"Gauntlet_Zc"],
                          Boat = boat_pinniped_vars[,"Gauntlet_Zc"],
                          Zone = zone_pinniped_vars[,"Gauntlet_Zc"], 
                          Haulout = haulout_pinniped_vars[,"Gauntlet_Zc"])

long_gauntlet_zc <- pivot_longer(gauntlet_zc, cols = "Base":"Haulout",
                                 names_to = "Scenario", values_to = "Gauntlet_Zc")

ggplot(data = long_gauntlet_zc) +
  geom_line(aes(x = Day, y = Gauntlet_Zc, color = Scenario), lwd = 1) + 
  labs(x = "Day of the Year", y = "California Sea Lions at the Gauntlet") +
  scale_color_manual(values = scenario.colors) + 
  pinniped_theme

# steller presence
gauntlet_ej <- data.frame(Day = (base_pinniped_vars[,"Day"] + (start_loop-1)),
                          Base = base_pinniped_vars[,"Gauntlet_Ej"],
                          Boat = boat_pinniped_vars[,"Gauntlet_Ej"],
                          Zone = zone_pinniped_vars[,"Gauntlet_Ej"], 
                          Haulout = haulout_pinniped_vars[,"Gauntlet_Ej"])

long_gauntlet_ej <- pivot_longer(gauntlet_ej, cols = "Base":"Haulout",
                                 names_to = "Scenario", values_to = "Gauntlet_Ej")

ggplot(data = long_gauntlet_ej) +
  geom_line(aes(x = Day, y = Gauntlet_Ej, color = Scenario), lwd = 1) + 
  labs(x = "Day of the Year", y = "Steller Sea Lions at the Gauntlet") +
  scale_color_manual(values = scenario.colors) + 
  pinniped_theme


```

## Discussion

Overall it seems like a boat-based harvest would make a lot of sense and possibly have a good positive impact on adult salmon survival and spawning in this system.

## Questions

