---
title: "Defining the Base Run"
subtitle: "Nisqually River"
date: "`r format(Sys.time(), '%B %d, %Y')`"
---

```{r setup, include=FALSE}

library(knitr)
library(flextable)
library(kableExtra)

fig.height <- 3
fig.width <- 6
font_size <- 12

```

### The Narrative

This model run is a scenario where managers or harvesters (or both) implement removals in the Gauntlet in an attempt to remove all pinnipeds that enter the Gauntlet zone.

### Run the Model

Parameters listed below are altered from the base run parameterization to simulate the management scenario. For this scenario we're enacting a zone exclusion management strategy.

```{r, set pars, include = FALSE}
source("Functions/01_predictFish.R")
source("Functions/makeArray.R")
source("Functions/createHarvestPlan.R")

# 02 Prep Data
source("Nisqually/02_Prep_Nisqually_Salmon_Data.R")

# 03 Set Model Parameters
source("Nisqually/03_Nis_set_pars_All.R")
```

```{r set scenario pars, message = FALSE, warning = FALSE}
zone_efficiency <- 0.8
zone_steepness <- 10
scenario <- "Zone"
scenario_sealion <- "Zone"
harvest_open <- start_loop
harvest_close <- end_loop
```

```{r, run loop, include = FALSE}
# 04 Initialize Variables
source("Nisqually/04_Nis_initialize_variables_All.R")

# 05 Loop Functions
source("Nisqually/05_salmonSpeciesUpdate_All.R")
source("Functions/decideForagingDestination.R")
source("Functions/collusion.R")
source("Functions/rungeKutta_3.R")
source("Functions/getHarvested.R")
source("Functions/learnX.R")
source("Functions/learnY.R")
source("Functions/type3FuncRes.R")
source("Functions/linearFuncRes.R")
source("Functions/updateLearning.R")

# 06 Run The Loop
source("Nisqually/06_The_Loop_Nis_All_fishing.R")

# 07 Plots
source("Functions/makePlots.R")
source("Functions/Plots_Pv.R")
source("Functions/Plots_Ej.R")
source("Functions/Plots_Zc.R")
source("Nisqually/07_Plots_All.R")
source("Functions/Plots_responses.R")
```