---
title: "Zone Exclusion Model Run"
subtitle: "Nisqually River"
date: "`r format(Sys.time(), '%B %d, %Y')`"
---

```{r setup, include=FALSE}

library(knitr)
library(flextable)
library(kableExtra)

fig.height <- 3
fig.width <- 6
font_size <- 12

```

### The Narrative

This model run is a scenario where managers or harvesters (or both) implement removals in the Gauntlet in an attempt to remove all pinnipeds that enter the Gauntlet zone.

### Run the Model

Parameters listed below are altered from the base run parameterization to simulate the management scenario. For this scenario we're enacting a zone exclusion management strategy.

```{r, set pars, include = FALSE}
source("Functions/01_predictFish.R")
source("Functions/makeArray.R")
source("Functions/createHarvestPlan.R")

# 02 Prep Data
source("Nisqually/02_Prep_Nisqually_Salmon_Data.R")

# 03 Set Model Parameters
source("Nisqually/03_Nis_set_pars_All.R")
```

```{r set scenario pars, message = FALSE, warning = FALSE}
zone_efficiency <- 0.25
zone_steepness <- 10
scenario <- "Zone"
harvest_days_pv <- start_loop:end_loop
harvest_days_ej <- start_loop:end_loop
harvest_days_zc <- start_loop:end_loop
num_harvesters <- NA
```

```{r, run loop, include = FALSE}
# 04 Initialize Variables
source("Nisqually/04_Nis_initialize_variables_All.R")

# 05 Loop Functions
source("Nisqually/05_salmonSpeciesUpdate_All.R")
source("Functions/decideForagingDestination.R")
source("Functions/collusion.R")
source("Functions/rungeKutta_3.R")
source("Functions/getHarvested.R")
source("Functions/learnX.R")
source("Functions/learnY.R")
source("Functions/type3FuncRes.R")
source("Functions/linearFuncRes.R")
source("Functions/updateLearning.R")

# 06 Run The Loop
source("Nisqually/06_The_Loop_Nis_All_fishing.R")

# 07 Plots
source("Functions/makePlots.R")
source("Functions/Plots_Pv.R")
source("Functions/Plots_Ej.R")
source("Functions/Plots_Zc.R")
source("Nisqually/07_Plots_All.R")
source("Functions/Plots_responses.R")
```

### Description of Parameterization

This scenario is focused on the effects of implementing an Exclusion Zone management strategy in the Nisqually River. Under this strategy, both seals and sea lions are removed from the Gauntlet by managers throughout all days of the model run. The proportion of pinnipeds that are removed is governed by an efficiency term which describes the asymptote of the type II response between the number of pinnipeds at the Gauntlet and the proportion of individuals removed. That response is shown below:

```{r efficiency plot, echo = FALSE, warning = FALSE, message = FALSE}
num_pinns <- 0:num_seals
plot(num_pinns, zone_efficiency * num_pinns/(zone_steepness + num_pinns), ylab = "Proportion of Pinnipeds Harvested", xlab = "Num Pinnipeds @ Gauntlet")
```

This management scenario is less feasible at Nisqually than at the Locks, so the efficiency parameter is much lower. The steepness parameter on the relationship between number of pinnipeds and efficiency of removals is also lower to represent the larger and more complex physical area for the pinnipeds to spread out in and be cryptic.
In this parameterization, more pinnipeds would be removed from the system than under incidental or boat-based take only. 

```{r harvest table, echo = FALSE}
kable(data.frame(Pv = sum(H), Ej = sum(H_ej), Zc = sum(H_zc)), caption = "Pinnipeds Removed") %>% kable_styling(full_width = F)
```

```{r pinniped harvest plot, echo = FALSE}
plot_H / plot_H_ej / plot_H_zc
```

Because of the increased removals, this scenario has an impact on pinniped behavior, presence at the Gauntlet, and survival. 

```{r pinnipeds at gauntlet, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 9}
plot_seals + plot_ej + plot_zc + plot_layout(guides = "collect", axes = "collect")
```

In the below plots, you can see the impact of removals on the learning process of individual harbor seals in the decline of the Gauntlet Probabilities.

```{r eaten to probs plots, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 9}
plot_H/plot_y/plot_probs + plot_layout(guides = "collect", axes = "collect")
```

### Salmon Response

The salmon response under this parameterization is as follows:

```{r, echo = FALSE}
salmon_fates <- data.frame(rbind(salmon_escapement, salmon_catch, salmon_consumed))
rownames(salmon_fates) <- c("Escape", "Catch", "Predated")
kable(salmon_fates) %>% kable_styling(full_width = F)
```

### Parameter Table

```{r parameter table, echo = FALSE, message = FALSE, warning = FALSE}
parameters <- data.frame(rbind(days, num_seals, num_zc, num_ej, zone_efficiency, zone_steepness, num_seals_2_copy, chum_escape_rate, gr_escape_rate, ln_escape_rate, Cmax, Cmax_zc, Cmax_ej, alpha))
colnames(parameters) <- c("Value")
kable(parameters) %>% kable_styling(full_width = F)
```
