---
title: "Parameter Manipulation - Nisqually"
output: ioslides_presentation
date: "`r Sys.Date()`"
---

```{r setup, message = FALSE, echo = FALSE, warning = FALSE}
knitr::opts_knit$set(root.dir = '~/GitHub/PinnipedCaseStudies')
library(knitr)
library(kableExtra)

fig.height <- 3
fig.width <- 6
font_size <- 12

source("Functions/01_predictFish.R")
source("Functions/makeArray.R")
source("Functions/createHarvestPlan.R")
source("Functions/decideForagingDestination.R")
source("Functions/collusion.R")
source("Functions/rungeKutta_3.R")
source("Functions/getHarvested.R")
source("Functions/learnX.R")
source("Functions/learnY.R")
source("Functions/type3FuncRes.R")
source("Functions/linearFuncRes.R")
source("Functions/updateLearning.R")
source("Functions/showManipulations.R")
```

## Purpose

This presentation is meant to document single parameter manipulations. The main comparison responses are the number of seals at the Gauntlet and the number of salmon escaped total of each species.

## The Base Run Realm

```{r base run realm, message = FALSE, echo = FALSE, warning = FALSE, fig.height = fig.height, fig.width = fig.width}

source("Nisqually/02_Prep_Nisqually_Salmon_Data.R")
source("Nisqually/03_Nis_set_pars_All.R")
source("Nisqually/04_Nis_initialize_variables_All.R")

source("Nisqually/Manipulations/assembleLegosNis.R")

(plot_seals + theme_classic()) / (eaten_sp_plot + theme_classic())

base_salmon_escapement <- data.frame(Run = "Base", salmon_escapement)
kable(salmon_escapement, caption = "Escaped Salmon") %>% kable_styling(full_width = F, font_size = font_size)
```

## num_seals

```{r num_seals, message = FALSE, echo = FALSE, warning = FALSE, fig.height = fig.height, fig.width = fig.width}

source("Nisqually/02_Prep_Nisqually_Salmon_Data.R")
source("Nisqually/03_Nis_set_pars_All.R")
num_seals_list <- seq(from = 1, to = 200, by = 99)
num_ej_list <- seq(from = 1, to = 200, by = 99)
num_zc_list <- seq(from = 1, to = 200, by = 99)

Escape <- data.frame(Seals = 0, Chum = 0, Chinook_GR = 0, Chinook_LN = 0)

for(i in 1:length(num_seals_list)){
  num_seals <- num_seals_list[i]
  num_ej <- num_ej_list[i]
  num_zc <- num_zc_list[i]
  source("Nisqually/04_Nis_initialize_variables_All.R")
  source("Nisqually/Manipulations/assembleLegosNis.R")
  Escape[i,] <- data_frame(Seals = num_seals, salmon_escapement)
}

result <- showManipulations(output = Escape, 150)
result[[1]]
result[[2]]

```

## prop_specialists

```{r prop_specialists, message = FALSE, echo = FALSE, warning = FALSE, fig.height = fig.height, fig.width = fig.width}

source("Nisqually/02_Prep_Nisqually_Salmon_Data.R")
source("Nisqually/03_Nis_set_pars_All.R")

prop_specialists_list <- seq(0, 1, 0.5)

Escape <- data.frame(specialist_prop = 0, Chum = 0, Chinook_GR = 0, Chinook_LN = 0)

for(i in 1:length(prop_specialists_list)){
  prop_specialists <- prop_specialists_list[i]
  source("Nisqually/04_Nis_initialize_variables_All.R")
  source("Nisqually/Manipulations/assembleLegosNis.R")
  Escape[i,] <- data_frame(specialist_prop = prop_specialists, salmon_escapement)
}

result <- showManipulations(output = Escape, 0.1)
result[[1]]
result[[2]]

```

## alpha (search and capture)

```{r alpha, message = FALSE, echo = FALSE, warning = FALSE, fig.height = fig.height, fig.width = fig.width}

source("Nisqually/02_Prep_Nisqually_Salmon_Data.R")
source("Nisqually/03_Nis_set_pars_All.R")

alpha_list <- seq(0, 0.6, 0.2)

Escape <- data.frame(Alpha = 0, Chum = 0, Chinook_GR = 0, Chinook_LN = 0)

for(i in 1:length(alpha_list)){
  alpha <- alpha_list[i]
  source("Nisqually/04_Nis_initialize_variables_All.R")
  source("Nisqually/Manipulations/assembleLegosNis.R")
  Escape[i,] <- data_frame(Alpha = alpha, salmon_escapement)
}

result <- showManipulations(output = Escape, 0.05)
result[[1]]
result[[2]]

```

## gamma (predator dependence)

```{r gamma, message = FALSE, echo = FALSE, warning = FALSE, fig.height = fig.height, fig.width = fig.width}

source("Nisqually/02_Prep_Nisqually_Salmon_Data.R")
source("Nisqually/03_Nis_set_pars_All.R")

gamma_list <- seq(-1, 0, 0.2)

Escape <- data.frame(Gamma = 0, Chum = 0, Chinook_GR = 0, Chinook_LN = 0)

for(i in 1:length(gamma_list)){
  gamma <- gamma_list[i]
  source("Nisqually/04_Nis_initialize_variables_All.R")
  source("Nisqually/Manipulations/assembleLegosNis.R")
  Escape[i,] <- data_frame(Gamma = gamma, salmon_escapement)
}

result <- showManipulations(output = Escape, -1)
result[[1]]
result[[2]]

```

## Cmax

```{r Cmax, message = FALSE, echo = FALSE, warning = FALSE, fig.height = fig.height, fig.width = fig.width}

source("Nisqually/02_Prep_Nisqually_Salmon_Data.R")
source("Nisqually/03_Nis_set_pars_All.R")

Cmax_list <- seq(from = 1, to = 21, by = 10)

Escape <- data.frame(Cmax_val = 0, Chum = 0, Chinook_GR = 0, Chinook_LN = 0)

for(i in 1:length(Cmax_list)){
  Cmax <- Cmax_list[i]
  Cmax_ej <- Cmax_list[i]
  Cmax_zc <- Cmax_list[i]
  source("Nisqually/04_Nis_initialize_variables_All.R")
  source("Nisqually/Manipulations/assembleLegosNis.R")
  Escape[i,] <- data_frame(Cmax_val = Cmax, salmon_escapement)
}

result <- showManipulations(output = Escape, 5)
result[[1]]
result[[2]]

```

## specialist_prob

```{r specialist_prob, message = FALSE, echo = FALSE, warning = FALSE, fig.height = fig.height, fig.width = fig.width}

source("Nisqually/02_Prep_Nisqually_Salmon_Data.R")
source("Nisqually/03_Nis_set_pars_All.R")

specialist_prob_list <- seq(from = 0, to = 1, by = 0.5)

Escape <- data.frame(specialist_prob_val = 0, Chum = 0, Chinook_GR = 0, Chinook_LN = 0)

for(i in 1:length(specialist_prob_list)){
  specialist_prob <- specialist_prob_list[i]
  source("Nisqually/04_Nis_initialize_variables_All.R")
  source("Nisqually/Manipulations/assembleLegosNis.R")
  Escape[i,] <- data_frame(specialist_prob_val = specialist_prob, salmon_escapement)
}

result <- showManipulations(output = Escape, 0.5)
result[[1]]
result[[2]]

```

## w (relative goodness of the Gauntlet)

```{r w, message = FALSE, echo = FALSE, warning = FALSE, fig.height = fig.height, fig.width = fig.width}

source("Nisqually/02_Prep_Nisqually_Salmon_Data.R")
source("Nisqually/03_Nis_set_pars_All.R")

w_list <- seq(from = 0, to = 1, by = 0.5)

Escape <- data.frame(w_val = 0, Chum = 0, Chinook_GR = 0, Chinook_LN = 0)

for(i in 1:length(w_list)){
  w <- w_list[i]
  source("Nisqually/04_Nis_initialize_variables_All.R")
  source("Nisqually/Manipulations/assembleLegosNis.R")
  Escape[i,] <- data_frame(w_val = w, salmon_escapement)
}

result <- showManipulations(output = Escape, 0.5)
result[[1]]
result[[2]]

```

## intercept_x_val

```{r intercept_x_val, message = FALSE, echo = FALSE, warning = FALSE, fig.height = fig.height, fig.width = fig.width}

source("Nisqually/02_Prep_Nisqually_Salmon_Data.R")
source("Nisqually/03_Nis_set_pars_All.R")

intercept_x_val_list <- seq(from = 0, to = 0.06, by = 0.02)

Escape <- data.frame(intercept_x_val_val = 0, Chum = 0, Chinook_GR = 0, Chinook_LN = 0)

for(i in 1:length(intercept_x_val_list)){
  intercept_x_val <- intercept_x_val_list[i]
  source("Nisqually/04_Nis_initialize_variables_All.R")
  source("Nisqually/Manipulations/assembleLegosNis.R")
  Escape[i,] <- data_frame(intercept_x_val_val = intercept_x_val, salmon_escapement)
}

result <- showManipulations(output = Escape, 0.01)
result[[1]]
result[[2]]

```

## steepness_y

```{r steepness_y, message = FALSE, echo = FALSE, warning = FALSE, fig.height = fig.height, fig.width = fig.width}

source("Nisqually/02_Prep_Nisqually_Salmon_Data.R")
source("Nisqually/03_Nis_set_pars_All.R")

steepness_list <- seq(from = 0, to = 3, by = 1)

Escape <- data.frame(steepness_val = 0, Chum = 0, Chinook_GR = 0, Chinook_LN = 0)

for(i in 1:length(steepness_list)){
  steepness <- steepness_list[i]
  source("Nisqually/04_Nis_initialize_variables_All.R")
  source("Nisqually/Manipulations/assembleLegosNis.R")
  Escape[i,] <- data_frame(steepness_val = steepness, salmon_escapement)
}

result <- showManipulations(output = Escape, 1)
result[[1]]
result[[2]]

```

## threshold_val_y

```{r threshold_val_y, message = FALSE, echo = FALSE, warning = FALSE, fig.height = fig.height, fig.width = fig.width}

source("Nisqually/02_Prep_Nisqually_Salmon_Data.R")
source("Nisqually/03_Nis_set_pars_All.R")

threshold_val_list <- seq(from = -10, to = 0, by = 5)

Escape <- data.frame(threshold_val_val = 0, Chum = 0, Chinook_GR = 0, Chinook_LN = 0)

for(i in 1:length(threshold_val_list)){
  threshold_val <- threshold_val_list[i]
  source("Nisqually/04_Nis_initialize_variables_All.R")
  source("Nisqually/Manipulations/assembleLegosNis.R")
  Escape[i,] <- data_frame(threshold_val_val = threshold_val, salmon_escapement)
}

result <- showManipulations(output = Escape, -5)
result[[1]]
result[[2]]

```

## threshold_x_specialist

```{r threshold_x_specialist, message = FALSE, echo = FALSE, warning = FALSE, fig.height = fig.height, fig.width = fig.width}

source("Nisqually/02_Prep_Nisqually_Salmon_Data.R")
source("Nisqually/03_Nis_set_pars_All.R")

threshold_x_specialist_list <- seq(from = -10, to = 0, by = 2)

Escape <- data.frame(threshold_x_specialist_val = 0, Chum = 0, Chinook_GR = 0, Chinook_LN = 0)

for(i in 1:length(threshold_x_specialist_list)){
  threshold_x_specialist <- threshold_x_specialist_list[i]
  source("Nisqually/04_Nis_initialize_variables_All.R")
  source("Nisqually/Manipulations/assembleLegosNis.R")
  Escape[i,] <- data_frame(threshold_x_specialist_val = threshold_x_specialist, salmon_escapement)
}

result <- showManipulations(output = Escape, -10)
result[[1]]
result[[2]]

```

## step

```{r step, message = FALSE, echo = FALSE, warning = FALSE, fig.height = fig.height, fig.width = fig.width}

source("Nisqually/02_Prep_Nisqually_Salmon_Data.R")
source("Nisqually/03_Nis_set_pars_All.R")

step_list <- seq(from = 0, to = 5, by = 1)

Escape <- data.frame(step_val = 0, Chum = 0, Chinook_GR = 0, Chinook_LN = 0)

for(i in 1:length(step_list)){
  step <- step_list[i]
  source("Nisqually/04_Nis_initialize_variables_All.R")
  source("Nisqually/Manipulations/assembleLegosNis.R")
  Escape[i,] <- data_frame(step_val = step, salmon_escapement)
}

result <- showManipulations(output = Escape, 0.5)
result[[1]]
result[[2]]

```

## decay

```{r decay, message = FALSE, echo = FALSE, warning = FALSE, fig.height = fig.height, fig.width = fig.width}

source("Nisqually/02_Prep_Nisqually_Salmon_Data.R")
source("Nisqually/03_Nis_set_pars_All.R")

decay_list <- seq(from = 0, to = 5, by = 1)

Escape <- data.frame(decay_val = 0, Chum = 0, Chinook_GR = 0, Chinook_LN = 0)

for(i in 1:length(decay_list)){
  decay <- decay_list[i]
  source("Nisqually/04_Nis_initialize_variables_All.R")
  source("Nisqually/Manipulations/assembleLegosNis.R")
  Escape[i,] <- data_frame(decay_val = decay, salmon_escapement)
}

result <- showManipulations(output = Escape, 0.5)
result[[1]]
result[[2]]

```

## num_seals_2_copy

```{r num_seals_2_copy, message = FALSE, echo = FALSE, warning = FALSE, fig.height = fig.height, fig.width = fig.width}

source("Nisqually/02_Prep_Nisqually_Salmon_Data.R")
source("Nisqually/03_Nis_set_pars_All.R")

num_seals_2_copy_list <- seq(from = 0, to = num_seals, by = num_seals/3)

Escape <- data.frame(num_seals_2_copy_val = 0, Chum = 0, Chinook_GR = 0, Chinook_LN = 0)

for(i in 1:length(num_seals_2_copy_list)){
  num_seals_2_copy <- num_seals_2_copy_list[i]
  source("Nisqually/04_Nis_initialize_variables_All.R")
  source("Nisqually/Manipulations/assembleLegosNis.R")
  Escape[i,] <- data_frame(num_seals_2_copy_val = num_seals_2_copy, salmon_escapement)
}

result <- showManipulations(output = Escape, 25)
result[[1]]
result[[2]]

```

## beta

```{r beta, message = FALSE, echo = FALSE, warning = FALSE, fig.height = fig.height, fig.width = fig.width}

source("Nisqually/02_Prep_Nisqually_Salmon_Data.R")
source("Nisqually/03_Nis_set_pars_All.R")

beta_list <- seq(from = 0, to = 20, by = 5)

Escape <- data.frame(beta_val = 0, Chum = 0, Chinook_GR = 0, Chinook_LN = 0)

for(i in 1:length(beta_list)){
  beta <- beta_list[i]
  source("Nisqually/04_Nis_initialize_variables_All.R")
  source("Nisqually/Manipulations/assembleLegosNis.R")
  Escape[i,] <- data_frame(beta_val = beta, salmon_escapement)
}

result <- showManipulations(output = Escape, 15)
result[[1]]
result[[2]]

```

## steepness_H

```{r steepness_H, message = FALSE, echo = FALSE, warning = FALSE, fig.height = fig.height, fig.width = fig.width}

source("Nisqually/02_Prep_Nisqually_Salmon_Data.R")
source("Nisqually/03_Nis_set_pars_All.R")

steepness_H_list <- seq(from = 0, to = 300, by = 100)

Escape <- data.frame(steepness_H_val = 0, Chum = 0, Chinook_GR = 0, Chinook_LN = 0)

for(i in 1:length(steepness_H_list)){
  steepness_H <- steepness_H_list[i]
  source("Nisqually/04_Nis_initialize_variables_All.R")
  source("Nisqually/Manipulations/assembleLegosNis.R")
  Escape[i,] <- data_frame(steepness_H_val = steepness_H, salmon_escapement)
}

result <- showManipulations(output = Escape, 200)
result[[1]]
result[[2]]

```

## efficiency (hunt)

```{r efficiency_H, message = FALSE, echo = FALSE, warning = FALSE, fig.height = fig.height, fig.width = fig.width}

source("Nisqually/02_Prep_Nisqually_Salmon_Data.R")
source("Nisqually/03_Nis_set_pars_All.R")

efficiency_list <- seq(from = 0, to = 0.5, by = 0.1)

Escape <- data.frame(efficiency_val = 0, Chum = 0, Chinook_GR = 0, Chinook_LN = 0)

for(i in 1:length(efficiency_list)){
  efficiency <- efficiency_list[i]
  source("Nisqually/04_Nis_initialize_variables_All.R")
  source("Nisqually/Manipulations/assembleLegosNis.R")
  Escape[i,] <- data_frame(efficiency_val = efficiency, salmon_escapement)
}

result <- showManipulations(output = Escape, 0.075)
result[[1]]
result[[2]]

```

## salmon natural mortality

```{r natural_mort, message = FALSE, echo = FALSE, warning = FALSE, fig.height = fig.height, fig.width = fig.width}

source("Nisqually/02_Prep_Nisqually_Salmon_Data.R")
source("Nisqually/03_Nis_set_pars_All.R")

natural_mort_list <- seq(from = 0, to = 0.001, by = 0.00025)

Escape <- data.frame(natural_mort_val = 0, Chum = 0, Chinook_GR = 0, Chinook_LN = 0)

for(i in 1:length(natural_mort_list)){
  natural_mort <- natural_mort_list[i]
  source("Nisqually/04_Nis_initialize_variables_All.R")
  source("Nisqually/Manipulations/assembleLegosNis.R")
  Escape[i,] <- data_frame(natural_mort_val = natural_mort, salmon_escapement)
}

result <- showManipulations(output = Escape, 0.0005)
result[[1]]
result[[2]]

```

## chum_escape_rate

```{r chum_escape_rate, message = FALSE, echo = FALSE, warning = FALSE, fig.height = fig.height, fig.width = fig.width}

source("Nisqually/02_Prep_Nisqually_Salmon_Data.R")
source("Nisqually/03_Nis_set_pars_All.R")

chum_escape_rate_list <- seq(from = 0, to = 0.1, by = 0.02)

Escape <- data.frame(chum_escape_rate_val = 0, Chum = 0, Chinook_GR = 0, Chinook_LN = 0)

for(i in 1:length(chum_escape_rate_list)){
  chum_escape_rate <- chum_escape_rate_list[i]
  source("Nisqually/04_Nis_initialize_variables_All.R")
  source("Nisqually/Manipulations/assembleLegosNis.R")
  Escape[i,] <- data_frame(chum_escape_rate_val = chum_escape_rate, salmon_escapement)
}

result <- showManipulations(output = Escape, 0.048)
result[[1]]
result[[2]]

```

## gr_escape_rate

```{r gr_escape_rate, message = FALSE, echo = FALSE, warning = FALSE, fig.height = fig.height, fig.width = fig.width}

source("Nisqually/02_Prep_Nisqually_Salmon_Data.R")
source("Nisqually/03_Nis_set_pars_All.R")

gr_escape_rate_list <- seq(from = 0, to = 0.1, by = 0.02)

Escape <- data.frame(gr_escape_rate_val = 0, Chum = 0, Chinook_GR = 0, Chinook_LN = 0)

for(i in 1:length(gr_escape_rate_list)){
  gr_escape_rate <- gr_escape_rate_list[i]
  source("Nisqually/04_Nis_initialize_variables_All.R")
  source("Nisqually/Manipulations/assembleLegosNis.R")
  Escape[i,] <- data_frame(gr_escape_rate_val = gr_escape_rate, salmon_escapement)
}

result <- showManipulations(output = Escape, 0.07)
result[[1]]
result[[2]]

```

## ln_escape_rate

```{r ln_escape_rate, message = FALSE, echo = FALSE, warning = FALSE, fig.height = fig.height, fig.width = fig.width}

source("Nisqually/02_Prep_Nisqually_Salmon_Data.R")
source("Nisqually/03_Nis_set_pars_All.R")

ln_escape_rate_list <- seq(from = 0, to = 0.2, by = 0.05)

Escape <- data.frame(ln_escape_rate_val = 0, Chum = 0, Chinook_GR = 0, Chinook_LN = 0)

for(i in 1:length(ln_escape_rate_list)){
  ln_escape_rate <- ln_escape_rate_list[i]
  source("Nisqually/04_Nis_initialize_variables_All.R")
  source("Nisqually/Manipulations/assembleLegosNis.R")
  Escape[i,] <- data_frame(ln_escape_rate_val = ln_escape_rate, salmon_escapement)
}

result <- showManipulations(output = Escape, 0.07)
result[[1]]
result[[2]]

```

