---
title: "Experiment: Boat Harvest Implementation"
subtitle: "Describing the model run when boat-based harvest is amplified above incidental levels"
date: "`r format(Sys.time(), '%B %d, %Y')`"
---

### The Narrative

This Model Run is for a scenario where managers open harvest of seals in the gauntlet by fishing vessels during the Coho fishery. This is modeled similarly to incidental fishery take but at a higher exploitation rate.  

### Run the Model

```{r, setup, include = FALSE}
library(knitr)
library(flextable)
library(kableExtra)
knitr::opts_knit$set(root.dir = '~/GitHub/PinnipedCaseStudies')
```

```{r, message = FALSE, warning = FALSE}

## Load Data Files and Setup Functions 
source("Functions/Prep_data_for_Salmon_functions.R")
source("Functions/Prep_data_for_Harvest_functions.R")

source("Functions/makeArray.R")
source("Functions/createHarvestPlan.R")

## Set Parameters and Create Variables
source("Functions/BaseRun_set_pars.R")

steepness_H <- 5 # how quick does it saturate (higher = slower)
efficiency <- 0.2 # what prop of seals are they capable of taking
min_fishers <- 13
max_fishers <- 25
fishery_open <- yday(as.Date("2023-09-10")) # coho fishery dates from 2023
fishery_close <- yday(as.Date("2023-11-17"))
boat_days <- fishery_open:fishery_close

source("Functions/BaseRun_initialize_variables.R")

harvest_plan <- createHarvestPlan(scenario = "Boat", 
                                  boat_days = boat_days,
                                  empty.array = oneDzeroes)

## Load Function Files
source("Functions/salmonSpeciesUpdate.R")
source("Functions/decideForagingDestination.R")
source("Functions/collusion.R")
source("Functions/rungeKutta.R")
source("Functions/getHarvested.R")
source("Functions/learnX.R")
source("Functions/learnY.R")

## Run the Loop
source("Models/The_Loop.R")

## Plots
source("Functions/Plots.R")
```

### Parameter Table

This scenario is focused on the effects of a different management strategy that changes the quantity of seal harvest. Removals occur on days when the coho fishery is open in the gauntlet. The harvest strategy is still boat-based like incidental harvest but it is more aggressive as it is focused on seal removal directly not incidentally as in the base run.

Removals occur from day `r salmon_days[1]` - `r salmon_days[length(salmon_days)]`.  
Removals are a type 2 function as follows:

```{r}
fishers <- 0:max_fishers
plot(fishers, getHarvested(day_plan = "Boat", list_gauntlet_seals = 1:num_seals, 
                           num_fishers = fishers, steepness = steepness_H, 
                           efficiency = efficiency, round = F), ylab = "Harvested Seals")
```

Here's the (kinda) full parameter list:
```{r, echo = FALSE, message = FALSE, warning = FALSE}
parameters <- data.frame(rbind(days, num_seals, zone_efficiency, num_seals_2_copy, sockeye_escape_rate, chinook_escape_rate, coho_escape_rate, min_fishers, max_fishers, fishery_open, fishery_close, sockeye_fish_rate, chinook_fish_rate, coho_fish_rate, natural_mort, Cmax, alpha))
colnames(parameters) <- c("Value")
kable(parameters) %>% kable_styling(full_width = F)
```

### Things to Note

The total escaped sockeye, chinook, and Coho are as follows under this parameterization:

```{r, echo = FALSE}
salmon_escapement <- data.frame(Sockeye = escape_sockeye[days], Chinook = escape_chinook[days],
                                Coho = escape_coho[days])
kable(salmon_escapement) %>% kable_styling(full_width = F)
```
