---
title: "Experiment Test: More Seals"
subtitle: "Making sure the model run ran right: Add more seals!!"
date: "`r format(Sys.time(), '%B %d, %Y')`"
---

### The Narrative

This Model Run is for a scenario where there are actually 150 seals in the area around the Gauntlet instead of the 20 that exist in the Base Run Realm.

### Run the Model

```{r, setup, include = FALSE}
knitr::opts_knit$set(root.dir = '~/GitHub/PinnipedCaseStudies')
```

```{r, message = FALSE, warning = FALSE}

## Load Data Files and Setup Functions 
source("Functions/Prep_data_for_Salmon_functions.R")
source("Functions/Prep_data_for_Harvest_functions.R")

source("Functions/makeArray.R")
source("Functions/createHarvestPlan.R")

## Set Parameters and Create Variables
source("Functions/BaseRun_set_pars.R")

num_seals <- 150

source("Functions/BaseRun_initialize_variables.R")

## Load Function Files
source("Functions/salmonSpeciesUpdate.R")
source("Functions/decideForagingDestination.R")
source("Functions/collusion.R")
source("Functions/rungeKutta.R")
source("Functions/getHarvested.R")
source("Functions/learnX.R")
source("Functions/learnY.R")

## Run the Loop
source("Models/The_Loop.R")

## Plots
source("Functions/Plots.R")
```

### Parameter Table

This scenario is focused on deviated values of:  

* num_seals (`r num_seals`)

Here's the (kinda) full parameter list:
```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
library(flextable)
library(kableExtra)
parameters <- data.frame(rbind(days, num_seals, num_seals_2_copy, sockeye_escape_rate, chinook_escape_rate, coho_escape_rate, min_fishers, max_fishers, fishery_open, fishery_close, sockeye_fish_rate, chinook_fish_rate, coho_fish_rate, natural_mort, Cmax, alpha))
colnames(parameters) <- c("Value")
kable(parameters) %>% kable_styling(full_width = F)
```

### Things to Note

In this model run, there are many more seals at the Gauntlet at the peak of salmon presence. In fact, all the seals eventually end up at the Gauntlet when there have been salmon present for long enough for them all to learn about it.

```{r, plot3, echo = FALSE, fig.height = 3, warning = FALSE}
plot_seals
```

[describe more things that are cool/important about this parameterization here]

END